Automatic Parallelization and Transparent Fault Tolerance

### 2016-06-15 pubs/tfp16/slides/slides.tex
add LAUR #, acknowledgements to slides

\title{Automatic Parallelization and Transparent Fault Tolerance}
%\subtitle{(Project article)}
\author{Kei Davis, Dean Prichard, \\\emph{David Ringo}, Loren Anderson, \\and Jacob Marks\\ \ \\}
%\date[4/26/2016]{Some Random Meeting \\ April 26, 2016}
\date{Trends in Functional Programming, June 8-10, 2016}
\LAUR{LA-UR-16-?????}

@@

>>>>

\title{Automatic Parallelization and Transparent Fault Tolerance}
%\subtitle{(Project article)}
\author{Kei Davis, Dean Prichard, \\\emph{David Ringo}, Loren Anderson, \\and Jacob Marks\\ \ \\}
%\date[4/26/2016]{Some Random Meeting \\ April 26, 2016}
\date{Trends in Functional Programming, June 8-10, 2016}
\LAUR{LA-UR-16-24056}

@@

\begin{frame}
  \frametitle{Acknowledgements}

  \footnotesize{Funding for this project has been provided by the DOE
    NNSA LANL Laboratory Directed Research and Development program
    award 20150845ER; the National Science Foundation Science,
    Technology, Engineering, and Mathematics Talent Expansion Program
    (NSF STEP) program for undergraduate students; and the Department
    of Energy Science Undergraduate Laboratory Internship (DOE SULI)
    program.}

  \vspace{0.2in}

  \footnotesize{Los Alamos National Laboratory is managed and operated
    by Los Alamos National Security, LLC (LANS), under contract number
    DE-AC52-06NA25396 for the Department of Energy’s National Nuclear
    Security Administration (NNSA).}
\end{frame}
